An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex
Fixing some notation in the Appendix

\section{Top-$k$ surrogate}
Throughout this section, consider the surrogate and discrete loss $L_2(u)_y~:=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell_2(r,y) = \Ind{y \not\in r} + \frac{|r \setminus \{y\}|}{k}$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.

@@

  Now, since we can restrict to the closed hypercube, we claim that we can rewrite the surrogate $L_2$ as 
  \begin{align*}
  	\inprod{p}{L_2(u)} &:= \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} + u_{[k+1]} \sum_{i=1}^k p_{[i]} \right) + 1 - \inprod{p}{u}
  \end{align*}

>>>>

\section{Top-$k$ surrogate}
Throughout this section, consider the surrogate and discrete loss $L_2(u)_y~:=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ and $\ell_2(r)_y = \Ind{y \not\in r} + \frac{|r \setminus \{y\}|}{k}$ given in Equations~\ref{eq:L-2-surrogate} and~\ref{eq:ell-2}, respectively.

@@

  Now, since we can restrict to the closed hypercube, we claim that we can rewrite the expected loss of $L_2$ as 
  \begin{align*}
  	\inprod{p}{L_2(u)} &= \frac{1}{k} \left( \sum_{i=1}^k (1 - p_{[i]}) u_{[i]} + u_{[k+1]} \sum_{i=1}^k p_{[i]} \right) + 1 - \inprod{p}{u}
  \end{align*}
